\documentclass{report}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{subfiles}
\usetikzlibrary{arrows}

\newtheorem{theorem}{Theorem}
\newtheorem{prop}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{Cor}{Corollary}
\newtheorem{myproof}{Proof}

\newtheorem{mydef}{Definition}
\DeclareMathOperator{\Ima}{Im}
\title{Which spheres are groups}
\author{Stefan Franssen \\4035844}
\usetikzlibrary{matrix}
\begin{document}
\maketitle
\tableofcontents{}
\chapter{Introduction}
\subfile{Chapter1}
\chapter{Algebras}
\subfile{Chapter2}
\chapter{Topological groups}
\subfile{Chapter3}
\chapter{Lie groups}
\subfile{Chapter4}
\chapter{$S^{n-1}$ is a topological group iff $\mathbb{R}^n$ is a ring}
\subfile{Chapter5}
\chapter{Vector Bundles}
\subfile{Chapter6}
\chapter{Topological K-theory}
\subfile{Chapter7}
\chapter{Complex Bott periodicity}
\subfile{Chapter8}
\chapter{Extending to a cohomology theory}
\subfile{Chapter9}
\chapter{$S^n$ is an H-space iff $n = 0,1,3,7$}
\subfile{Chapter10}
\chapter{Splitting principle}
prop 2.23
prop 2.24
Theorem 2.25
Example 2.26
Proof of splitting principle
\chapter{Possible: Real Bott periodicity and linear independent vector fields on a sphere}
\chapter{ToDoList}
We keep a todo list per chapter
\section{Introduction}
Making a more extensive introduction, show an overview of the thesis and explain what we will do per part.
\section{Algebras}
Show examples. Explain relationships between types of algebra.
\\Show the proof of the Cayley-Hamilton theorem
\\Show the there only exists up to isomorphism four alternative finite dimensional real division algebras, proof by zorn 1931?
\\fix equation indentation
\section{Topological groups}
Give some more examples.
\section{Lie groups}
introduce lie groups, maybe before topological groups?
\section{$S^ {n-1}$ is a topological group iff $\mathbb{R}^n$ is a ring}
show that if $S^{n-1}$ is a topological group there is a vector space that makes the multiplication bilinear?
\section{vector bundles}
Depending on what all gets added, add extra theorems which will be needed later.
\section{Topological K-theory}
Show that multiplication is well defined.
\\blz 25: might?? prove it later

\section{Extending to a cohomology theory}
hoofdstuk schrijven
\section{$S^n$ is an H-space iff $n = 0,1,3,7$}
Show naturality
\\fix the equation indentation
\section{complex Bott periodicity}
\section{Splitting principle}
write chapter
\section{Literature list}
Make a literature list
\section{General work}
Reread the books of Hatcher. Find if it contains new things to add to the thesis.
\\Fix typos, spelling and grammar errors etc.
\\Add more texts between the theorems/proof structure, explain their meaning in an intuitive way give more examples.
\\Add more on the algebraic side of the story.
\\Heel veel hence op blz 8 
\\blz 18 goed bekijken (zei je zelf)
\\proof 18 op blz 23 is een lastig geformuleerde zin
\\namen van personen met hoofdletters, denk aan Hopf, Frobenius, Hurwitz

\section{stack}
Write the chapter extending to a cohomology theory.
\\Proof of existence of Adams operations, proof of naturality must be done
\\In bott periodicity theorem, why unique element in $\tilde{K}(X \wedge Y)$
\\Write chapter on the splitting principle.
\\Maybe add more info on composition algebras, proof theorem.
\\More info on lie groups
\\Fix literature list
\end{document}