\documentclass[../Thesis.tex]{subfiles}
\begin{document}
In topological K-theory we develop an Functor $K$ which maps compact Hausdorff topological spaces to rings. So given a topological space $X$ we are going to develop a ring $K(X)$. A ring has to obey the following axioms:
\begin{itemize}
\item $K(X)$ is an abelian group under addition.
\item $K(X)$ is a monoid under multiplication, eg $\cdot$ is associative and there is an identity.
\item multiplication is distributive with respect to addition: $a\cdot ( b+c) = (a\cdot b) + (a \cdot c)$ and $(b+c)\cdot a = (b\cdot a) + (c \cdot a)$
\end{itemize}

So first we need a abelian group for addition. After that, we need an multiplication operation which distributes over the addition. We shall show that the direct sum of vector bundles on $X$ can be made into an abelian group, and that tensoring vector bundles over $X$ defines a multiplication.
\\Furthermore, to be a functor, morphisms from one topological space into the other should induce morphisms from one ring to the other. In this case, the morphisms from one topological space to the other is a continuous function, and the morphisms from the one ring to the other are ring homomorphisms. In other words, the following diagram commutes:\\\newline

\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=4em,minimum width=2em]
  {
     X & Y \\
     K(X) & K(Y) \\};
  \path[-stealth]
    (m-1-1) edge node [above] {$F$} (m-1-2)
    (m-1-1) edge node [left] {$K$} (m-2-1)
    (m-2-1) edge node [below] {$F_*$} (m-2-2)
    (m-1-2) edge node [right] {$K$} (m-2-2);
\end{tikzpicture}    
\section{Direct sum of vector bundles induces an abelian group}
We start with a few basic constructions. First we fix a compact Hausdorff space $X$. It is convenient to take a slightly broader definition of vector bundles in this chapter. We allow fibers of a vector bundle $p : E \rightarrow X$ to be vector spaces of different dimensions. There still should be local trivializations $h: p^{-1}(U) \rightarrow U \times \mathbb{C}^n$. 
\begin{lemma}
Dimensions of fibers of vector bundles are locally constant.
\end{lemma}
\begin{myproof}
Suppose that we have an open cover $\mathcal{U} = \{U_\alpha\}$ of $X$. Then we can split every open $U_\alpha$ in $\mathcal{U}$ into connected components $V_{\alpha, \beta}$. This gives another open cover $\mathcal{V}$.
\\Then note that for any $V_{\alpha, \beta}$ the space $V_{\alpha, \beta} \times \mathbb{K}^n$ has constant dimension, due to dimension being locally constant in $V_{\alpha, \beta}$ and $\mathbb{K}^n$ having dimension $n$.
\\Now suppose that we have two opens $V_1,V_2$ such that $p^{-1}(V_1) \cap p^{-1} (V_2) = W$ is non empty. Then we have two homeomorphisms $p : W \rightarrow p(W) \subset V_1$ and $p : W \rightarrow p(W) \subset V_2$. Hence $W$ has the same dimension as $V_1$ and $V_2$. Thus they are equal. This shows that dimension is locally constant.
\end{myproof}
We now define a equivalence relation on the set of all vector bundles. 
\begin{mydef}
We call two vector bundles $E_1$ and $E_2$ equivalent, $E_1 \sim E_2$ iff there exist trivial vector bundles $\epsilon^n, \epsilon^m$ of dimension $n$ and $m$ such that $E_1 \oplus \epsilon^n \approx E_2 \oplus \epsilon^m$
\end{mydef}
We shall show that the equivalence classes of $\sim$ form an abelian group.
\begin{theorem}
The equivalence classes of $\sim$ form an abelian group with the operation $\oplus$.
\end{theorem}
We define $[E_1] \oplus [E_2] = [E_1 \oplus E_2]$. This is clearly closed since any direct sum of vector bundles is again a vector bundle. It is also associative and the class of the trivial bundle $[\epsilon^0]$ forms the identity $[E_1] + [\epsilon^0] = [E_1 \oplus \epsilon^0] = [E_1]$. Thus the only thing we need to show is that there exist inverses.
\\We have shown that if for a vector bundle $E$ all the fibers have the same dimension $n$, there exist an vector bundle $E'$ such that their direct sum is a trivial vector bundle.
\\Now suppose that we have a vector bundle $p: E \rightarrow X$. We define $X_i = \{ x \in X| dim p^{-1} (x) = i\}$. This is a disjoint set in $X$, is open and hence forms an open cover. By compactness we can extract a finite subcover, but we cannot leave any non open cover out due to every open being disjoint from the rest. Hence there are only a finite amount of such $X_i$. We can find for each such $X_i$ a vector bundle $E'_i$ such that the direct sum of $p^{-1} X_i \oplus E'_i$ is trivial. These $E'_i$ together can then be made the fibers of a vector bundle over $X$ and we have found our inverse. This forms an abelian group $\tilde{K}(X)$. We shall construct $K(X)$ by using a stronger equivalence relation $\approx_s$.
\begin{mydef}
We call two vector bundles $E_1, E_2$ over $X$ stably isomorphic, $E_1 \approx_s E_2$ if $E_1 \oplus \epsilon^n \approx E_2 \oplus \epsilon ^n$
\end{mydef}
Note that if $E_1 \approx_s E_2$ then $E_1 \sim E_2$. Now we construct the abelian group $K(X)$ using $\approx_s$. We cannot have inverses in the same way as in $\tilde{K}(X)$ as two positive vector bundles cannot be added to form the zero dimensional trivial vector bundle. Thus we seek another property. Observe the following: 
\begin{lemma}
If $E_1 \oplus E_2 \approx_s E_1 \oplus E_3$ then $E_2 \approx_s E_3$.
\end{lemma}
\begin{myproof}
We know that $E_1 \oplus E_2 \approx_s E_1 \oplus E_3$ and we know that for $E_1$ there exists an $E'_1$ such that $E_1 \oplus E'_1 \approx \epsilon^n$ for some $n$. Now add this $E'_1$ to both sides of the first equation. This yields
$E'_1 \oplus E_1 \oplus E_2 \approx \epsilon^n \oplus E_2 \approx_s E_3 \oplus \epsilon ^n$. And thus $E_2 \approx_s E_3$.
\end{myproof}
We will use formal differences of vector bundles to form an abelian group. Notice that the zero element is equivalent to $E-E$ for any vector bundle $E$. 
\begin{theorem}
$K(X) = \tilde{K}(X) \oplus \mathbb{Z}$
\end{theorem}
\begin{myproof}
Since $\approx_s$ was a stronger equivalence relation, we can find a natural homomorphism $K(X) \rightarrow \tilde{K}(X)$. Notice that the homomorphism is surjective, and the kernel consist of elements of the form $\epsilon^m - \epsilon^n$. This subgroup of $K(X)$ is isomorphic to $\mathbb{Z}$. 
\end{myproof}
\section{Tensoring vector bundles induces a multiplication}
We have just defined the additive structure of $K(X)$ and are going to work on the multiplicative structure of $K(X)$. If we have two elements of $K(X)$, namely $E_1, E_2$, we define their product as follows $E_1 \otimes E_2$. Since the elements of $K(X)$ are in general represented by differences of vector bundles $E - E'$ we can define their product as follows:

\begin{equation} 
(E_1 - E'_1)(E_2 - E'_2) = E_1 \otimes E_2 - E_1 \otimes E'_2 - E'_1 \otimes E_2 + E'_1 \otimes E'_2
\end{equation}

Notice that tensoring is associative. distributively follows from the definition. All we have to show is that there exists an identity. $\epsilon^1$ is the identity by $\epsilon^1 \otimes ( E - E') = \epsilon^1 \otimes E - \epsilon \otimes E'= E - E'$. By commutativity $\epsilon^1$ is the multiplicative identity. Also notice that $\epsilon^n \otimes E$ gives $n$ copies of $E$ hence we can abbreviate $\epsilon^n$ by $n$ and let $nE$ stand of $n$ copies of $E$.
\\Now we want to show that this multiplication is well defined. Suppose that $E_1, E_2$ come from the same equivalence class, and we have another element $E_3$. Then consider $E_1 \otimes E_3$ and $E_2 \otimes E_3$. We can both add them up $(E_1 + \epsilon^n) \otimes E_3$ and $(E_2 + \epsilon^m) \otimes E_3$. These are equivalent to the first statement, however, this also yields $E_1 \otimes E_3 + \epsilon^n \otimes E_3$. And also $E_2 \otimes E_3 + \epsilon^m \otimes E_3$. These terms are equal since we multiplied the same element of $K(x)$ by $E_3$. However, the last part is equivalent to zero, hence $E_1 \otimes E_3$ is equivalent to $E_2 \otimes E_3$. We can exactly mirror this argument for the other side of multiplication. This shows that multiplication is well defined. As we will see in the next section, continuous maps induce ring homomorphisms. If we take the map which maps $X$ to $x_0 \in X$ this comes down to restricting vector bundles over the fibers to $x_0$. Its kernel is $\tilde{K}(X)$. Hence it is an ideal. Then $\tilde{K}(X)$ obeys all the ring axioms except it might not have an identity element.
\section{Continuous maps induce ring homomorphisms}
Given two compact Hausdorff spaces $X, Y$ and a continuous map between them. As we have seen, a map $f: X \rightarrow Y$ induces a map in vector bundles $f^*: E_Y \rightarrow E_X$. We have seen that $f^* (E_1 \oplus E_2) = f^*(E_1) \oplus f^*(E_2)$ and $f^*(E_1 \otimes E_2) = f^*(E_1) \otimes f^*(E_2)$ hence $f^*$ is a homomorphism. Further more $(fg)^* = g^* f^*$, $1^* = 1$. Thus $K$ obeys all the required relations for a functor. 

\section{Extra properties of $K(X)$}
These properties will be proved in later chapters
\subsection{External product}
We define the external product $\mu : K(X) \otimes K(Y) \rightarrow K(X \times Y)$ to be $\mu( a \otimes b) = p_1^*(a) p_2^*(b)$ where $p_1$ and $p_2$ are the projects of $X \times Y$ onto $X$ and $Y$. Notice that we tensor rings. The product of $a \otimes b \cdot c \otimes d$ is defined to be $ a \cdot c \otimes b \cdot d$.
\subsection{The fundamental Product theorem}
Theorem: The homomorphism $\mu:K(X) \otimes \mathbb{Z}[H]/(H-1)^2 \rightarrow K(X \times S^2)$ is an isomorphism of rings for all compact Hausdorff $X$.
\\We will not proof this theorem here, as it is a detour from our goal. For a proof we refer to \cite{VBKT}
\\This theorem yields directly the following corollary by taking $X = \{0\}$:
\\$\mathbb{Z}[H]/(H-1)^2 \rightarrow K(S^2)$ is an isomorphism of rings. This implies directly that $K(S^2) = \mathbb{Z}$
\subsection{Complex Bott periodicity}
The Bott periodicity theorem for complex vector bundles states that $\beta: \tilde{K}(X) \rightarrow \tilde{K}(S^2 X)$ with $\beta(a) = (H-1) * a$ is an isomorphism for all compact Hausdorff $X$.
\\As a corollary we have that $\tilde{K}(S^{2n + 1}) = 0$ and $\tilde{K}(s^{2n}) = \mathbb{Z}$.
\subsection{K-theory as a Cohomology}
We can make K-theory into a cohomology theory, by defining $\tilde{K}^{-n} (X) = \tilde{K}(S^n X)$. This obeys the axioms of cohomology. This will be shown in the chapter Extending to a cohomology theory. We then set $K^{-n}(X) = K(\Sigma^n X)$, where $\Sigma$ is the reduced suspension, i.e. where we send the north and south pole to the same point.
\subsection{The Splitting Principle}
Given a vector bundle $E \rightarrow X$ with $X$ compact Hausdorff space, there is a compact Hausdorff space $F(E)$ and a map $: F(E) \rightarrow X$ such that induced map $p^* : K^*(X)  \rightarrow K^*(F(E))$ is injective and $P^*(E)$ splits as a sum of line bundles. For a proof of the splitting principle we refer to \cite{VBKT}
\end{document}
